\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage[nodayofweek]{datetime}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}

\input{skypesymbol}
\input{getenv}

\moderncvstyle{classic}
\moderncvcolor{blue}
\nopagenumbers{}

\name{Jacek}{Szubert}
\address{ul. Raclawicka 69/4}{53-149 Wrocław}{Poland}
\phone[mobile]{+48~791~379~682}
\email{jacek.szubert@gmail.com}
\extrainfo{\skypesymbol \href{skype:szubert.jacek}{szubert.jacek}}
\social[linkedin]{jacek-szubert-16b76370}
%\photo[64pt][0.4pt]{picture}

\begin{document}
\makecvtitle
\section{Experience}
\cventry{2015--still}{DevOps Engineer}{SoftServe}{Wrocław (Poland)}{}{Used technologies:
\begin{itemize}
    \item[--]Amazon Web Services (AWS) stack: CloudFormation, Auto Scaling, Virtual Private Cloud (VPC),%
        Elastic Compute Cloud (EC2), Simple Storage Service (S3) and other.
    \item[--]Docker.
    \item[--]Chef.
    \item[--]HAProxy.
\end{itemize}
}
\cventry{2013--2015}{Software Integration Engineer (SCM)}{Nokia / Nokia Solutions and Networks}%
    {Wrocław (Poland)}{}{Maintaining and developing continous integration systems, as a technical leader, for two projects:
\begin{itemize}
    \item[--]Administration of physical (HP Proliants, HP Blades, NetApp) and virtualised (in Eucalyptus \& S3 (compatible with Amazon Web Services (AWS)),%
        Citrix XenServer and VMware vSphere technologies) servers and storages.
    \item[--]Administration of RHEL and Debian based Linux systems, including usage of tools for automated management like Ansible.
    \item[--]Scripting in Bash and Python.
    \item[--]Developing and optimizing continous integration flows (Jenkins, SVN, GIT) and release processes of C/C++ and Java projects.
    \item[--]Quality assurance - analysis using SonarQube and tools for C/C++, preparation for TL9000 audit.
    \item[--]Supporting developers and testers in their daily activities.
    \item[--]Taking over a project from other company, responsible both for competence and infrastructure transfer.
\end{itemize}
}
\cventry{2012}{OSS Technical Support -- internship}{Nokia Siemens Networks}{Wrocław (Poland)}{}%
    {Local laboratory administration, basic configuration and verification of OSS systems.}
\subsection{Miscellaneous}
\cventry{2011--still}{Administration of own web page and discussion forum}{}{}{}{}

\section{Education}
\cventry{2013--2015}{Master's degree}{Wrocław University of Technology}{}{}{Telecommunication --- Mobile Networks.}
\cventry{2009--2013}{Bachelor's degree}{Wrocław University of Technology}{}{}%
    {Electronics and Telecommunication --- Information and Communication Networks.}
\cventry{2009--2013}{Vocational Technical High School}{CKU}{Częstochowa}{}{Occupational safety and health.}

\section{Languages}
\cvitemwithcomment{english}{professional working proficiency}{IELTS}
\cvitemwithcomment{polish}{native}{}

\section{Skills}
\cvitem{administration}{Linux (RHEL and Debian based distributions).}
\cvitem{scripting}{Bash, Python.}
\cvitem{CVS}{Subversion, GIT.}
\cvitem{CM}{Ansible, Chef, basics of Puppet.}
\cvitem{CI}{Jenkins.}
\cvitem{code analysis}{SonarQube and related tools.}
\cvitem{virtualization and cloud computing}{
    \begin{itemize}
        \item[--] Amazon Web Services (AWS).
        \item[--] Citrix XenServer.
        \item[--] VMware vSphere.
        \item[--] Docker, Vagrant.
    \end{itemize}}
\cvitem{networking}{Practical understanding of TCP/IP networks, configuring network elements, troubleshooting.}
\cvitem{project management tools}{Redmine, JIRA.}
\cvitem{programming}{Basics of C++.}
\cvitem{databases}{Basics of SQL and PL/SQL.}

\section{Trainings and certifications}
\cvitem{embedded}{Designing Embedded Systems with Yocto (Doulos).}
\cvitem{networking}{Cisco Certified Network Associate.}
\cvitem{english}{IELTS general training certification (C1).}

\section{Other}
\cvlistitem{Driving licence, category B.}

\section{Interests}
\cvlistitem{Scorpiones (Animalia, Arachnida).}
\cvlistitem{Snooker.}
\cvlistitem{Space exploration.}

\newdateformat{mydate}{\THEDAY\ \monthname[\THEMONTH] \THEYEAR}

\getenv[\cvpl]{cvpl}
\ifdefstring{\cvpl}{true}{
    \cfoot{\footnotesize{I hereby agree for processing the following personal information strictly for%
    the purposes of job recruitment \newline in accordance with the regulation for the protection of%
    personal data passed on 29.08.1997, Dz.U nr 133 poz. 883.}\newline\hspace{1in}{\tiny{\shortdate\today}}}
}{
    \cfoot{\tiny{\shortdate\today}}
}

\end{document}
